Many-spin entanglement in multiple quantum NMR with a dipolar-ordered initial state

### 2020-05-16 manuscript.tex
Fix hl areas

The quantum Fisher information describes the quickness of a change of quantum states determined by a density matrix in response to a change of some parameter. 
In MQ NMR spectroscopy, that parameter is the phase increment between the radio-frequency (rf) pulses, irradiating the system on the preparation and mixing periods of the MQ NMR experiment~\cite{Baum_1985}. 
The phase increment is proportional to the duration of the evolution period that leads to the separation of the signals,
corresponding to MQ NMR coherences of different orders, and allows obtaining the total MQ NMR spectrum.
Using the quantum Fisher information (QFI)~\cite{Liu_2014} for the analysis of the MQ NMR spectra, one can extract important information about many-spin entanglement.
The point is that there is a relation between the second moment of the MQ NMR spectrum~\cite{Khitrin_1997} and the quantum Fisher information~\cite{G_rttner_2018,Doronin_2019}.
Moreover, the second moment of the MQ NMR spectrum provides a lower bound on the quantum Fisher information~\cite{G_rttner_2018}.
This means that the MQ NMR spectroscopy is a valuable method for solving quantum information problems.

>>>>

The quantum Fisher information describes the quickness of a change of quantum states determined by a density matrix in response to a change of some parameter. 
In MQ NMR spectroscopy, that parameter is the phase increment between the radio-frequency (rf) pulses, irradiating the system on the preparation and mixing periods of the MQ NMR experiment~\cite{Baum_1985} 
that leads to the separation of the signals, corresponding to MQ NMR coherences of different orders, and allows obtaining the total MQ NMR spectrum. 
The phase increment is proportional to the duration of the evolution period.
Using the quantum Fisher information (QFI)~\cite{Liu_2014} for the analysis of the MQ NMR spectra, one can extract important information about many-spin entanglement.
The point is that there is a relation between the second moment of the MQ NMR spectrum~\cite{Khitrin_1997} and the quantum Fisher information~\cite{G_rttner_2018,Doronin_2019}.
Moreover, the second moment of the MQ NMR spectrum provides a lower bound on the quantum Fisher information~\cite{G_rttner_2018}.
This means that the MQ NMR spectroscopy is a valuable method for solving quantum information problems.
